Investigation into Racial and Sexual Bias against Officers within Chicago Police Departments

### 2024-02-15 paper/paper.qmd
Cleaned up paper figure formatting  -ilq

---
title: "Inquires in Racial and Sexual Disparities among Chicago Police Department"
# subtitle: "My subtitle if needed"
author: 
  - Thu Dong 
  - Siddharth Arya 
  - Hyuk Jang 
thanks: "Code and data are available at: https://github.com/sid19arya/Police-Award-Nomination-Paper-Reproduction. Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-5nym-9g31" 
date: today
date-format: long
abstract: "Racial and Gender Disparities within police departments is an insufficiently investigated phenomenon. This paper replicates an investigation into racial and gender bias among officers within the Chicago Police Department and conducts further investigation into the discrimination faced by minority police officers in regard to receiving awards for their work. Although the replication portion finds convincing evidence of such discrimination, our investigations were inconclusive in the matter. In any case, this appears to motivate the police department to counterbalance promotion and advancement to control such disparities."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Investigation into Racial and Sexual Bias against Officers within Chicago Police Departments"
# subtitle: "My subtitle if needed"
author: 
  - Thu Dong 
  - Siddharth Arya 
  - Hyuk Jang 
thanks: "Code and data are available at: https://github.com/sid19arya/Police-Award-Nomination-Paper-Reproduction. Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-5nym-9g31" 
date: today
date-format: long
abstract: "Racial and Gender Disparities within police departments is an insufficiently investigated phenomenon. This paper replicates an investigation into racial and gender bias among officers within the Chicago Police Department and conducts further investigation into the discrimination faced by minority police officers in regard to the quantity of award nominations they recieve. Although the replication portion finds convincing evidence of such discrimination, our investigations were inconclusive in the matter. In any case, this appears to motivate the police department to counterbalance promotion and advancement to control such disparities."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
